decompr: GVC decomposition in R

### 2015-01-29 draft.Rnw
line breaks by sentence

\section{Data}
\label{sec:data}
Two data sets are included in the package, one real world data set, and one minimal fictional data for training purposes.
The former is the WIOD regional Inter-Country Input Output table for the year 2011 \parencite{timmer2012world}. 
The latter is a fictional 3-country 3-sector data set is included, which we will use throughout this article to exemplify
the mechanics of the package.

>>>>

\section{Data}
\label{sec:data}
Two data sets are included in the package, one real world data set, and one minimal fictional data, for training surposes.
The forme is the WIOD regional Inter-Country Input Output tables for the year 2011 \parencite{timmer2012world}. 
The later, a fictional 3-country 3-sector data set is included, which we will use throughout this article to exemplify the mechanics of the package.
